---
title: "BigMC"
author: "Dottie"
date: "2/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Get an estimated demand curve for Big Macs

```{r}
BigMCdata = read.csv('BigMCDemandDataSet.csv')
attach(BigMCdata)
names(BigMCdata)
```

Plot the data

```{r}
plot(demand,price)
```

x axis = demand
y axis = price

Fit a demand line to these data.

```{r}
priceOne = 4.95

model1 = lm(price~demand)
summary(model1)
plot(demand,price)
abline(model1)

abline(h = priceOne, col='red')
```

lm = linear model
lm(y axis, x axis)

Price Elasticity is the percent change in quantity demanded divided by the percent change in price.

The marginal revenue (MR) of any product is the additional revenue for sales of one additional Big MC.

It turns out that marginal revenue is related to price elasticity by: 

MR = price * (1 + elasticity)/elasticity

At McDonalds marginal revenue (MR) = marginal cost (MC)

Elasticity of Demand
E = slope of demand at price P * (price/quantity)

Demand = (price - intercept)/slope

```{r}
slope = model1$coefficients[2]
intercept = model1$coefficients[1]
demanded = (priceOne-intercept)/slope

E = slope*priceOne/demanded

MR = priceOne * abs((1+E)/E)

print(paste('price = ',priceOne))
print(paste('demanded = ',demanded))

print(paste('elasticity =', round(E,2)))
print(paste('MR = ', round(MR,2)))
```

Slope
y = mx + b

abs = absolute value

MR = $1.41/Big Mac, they make $1.41 for every Big Mac made.

Adding round gets rid of the many numbers after the decimal place.

Profit for Big Mac:

Profit = price - cost = 4.5 - MC

```{r}
profit = priceOne - MR
print(paste('profit =', profit))
```

